Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/composition.tex
grammar fix composition.tex

We also demonstrate that properties of certified
components maintain a crucial separation invariant within circuits
using methods developed in Section \ref{section-automation-logic}.
Specifically, we show that within a circuit $\prog$, the views of each
client remain probabilistically independent of the other client's
secrets, i.e., $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
%\quad \text{and} \quad
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$.
Through certification of decodings we can finally obtain $\NIMO$ in
circuits as in Theorems \ref{theorem-gmw-NIMO} and
\ref{theorem-ygc-NIMO}.

@@

Now we demonstrate that certified gates preserve the desired invariant
during execution in arbitrary circuit contexts.That is, where
$\iov(\prog) = S \cup V$, we show that
$\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$ are preserved prior to
decoding.  We formulate this in terms of pre-~and post-conditions of
gate evaluation. Proofs omitted here are provided in Appendix
\ref{section-proofs}.
\begin{lemma}[GMW Gate Invariant]
  \label{lemma-gmw-preservation}
  Given well-typed $\prog_1;E[\mathit{gate}(\ttt{"g"},v_1,v_2)]$ for certified $\mathit{gate}$ where:
  $$
  \config{\prog_1}{E[\mathit{gate}(\ttt{"g"},v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
  $$
  If we have the following preconditions, where $\iov(\prog_1) = S \cup V$:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
  \item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
  \end{enumerate}
  then we have as a postconditions, where $\iov(\prog_1;\prog_2) = S \cup V'$:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progd(\prog_1;\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$
  \item $\sep{\progd(\prog_1;\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$
  \end{enumerate}
\end{lemma}

>>>>

We also demonstrate that properties of certified
components maintain a crucial separation invariant within circuits
using methods developed in Section \ref{section-automation-logic}.
Specifically, we show that within a circuit $\prog$, the views of each
client remain probabilistically independent of the other client's
secrets, i.e., $\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
%\quad \text{and} \quad
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$.
Through certification of decodings, we can finally obtain $\NIMO$ in
circuits as in Theorems \ref{theorem-gmw-NIMO} and
\ref{theorem-ygc-NIMO}.

@@

Now we demonstrate that certified gates preserve the desired invariant
during execution in arbitrary circuit contexts. That is, where
$\iov(\prog) = S \cup V$, we show that
$\sep{\progd(\prog)}{S_{\{1\}}}{V_{\{2\}}}$ and
$\sep{\progd(\prog)}{S_{\{2\}}}{V_{\{1\}}}$ are preserved prior to
decoding.  We formulate this in terms of pre-~and post-conditions of
gate evaluation. Proofs omitted here are provided in Appendix
\ref{section-proofs}.
\begin{lemma}[GMW Gate Invariant]
  \label{lemma-gmw-preservation}
  Given well-typed $\prog_1;E[\mathit{gate}(\ttt{"g"},v_1,v_2)]$ for certified $\mathit{gate}$ where:
  $$
  \config{\prog_1}{E[\mathit{gate}(\ttt{"g"},v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[v]}
  $$
  If we have the following preconditions, where $\iov(\prog_1) = S \cup V$:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progd(\prog_1)}{S_{\{2\}}}{V_{\{1\}}}$
  \item $\sep{\progd(\prog_1)}{S_{\{1\}}}{V_{\{2\}}}$
  \end{enumerate}
  then we have as a postconditions, where $\iov(\prog_1;\prog_2) = S \cup V'$:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progd(\prog_1;\prog_2)}{S_{\{2\}}}{V'_{\{1\}}}$
  \item $\sep{\progd(\prog_1;\prog_2)}{S_{\{1\}}}{V'_{\{2\}}}$
  \end{enumerate}
\end{lemma}
